Dynamic Knapsack Problem

### 2021-04-30 Manuscript/Manuscript.tex
working on simulation - there are some issues with timeline

\subsubsection{Action Constraints}
\label{action constraints}
\begin{itemize}
    \item Tracks PPE Usage  
    \begin{itemize}
    		\item ($U_{pdc}$ - usage of PPE $p$ per patient difficulty $d$, CPU $c$)
    \end{itemize}
        \begin{equation} 
			(\sum_{mdc}ps_{tmdc} + \sum_{mdc}sc_{tmdc} + \sum_{tmdc} rsc_{tt'mdc} )U_{pdc} = uu_{tp}\ \quad \forall tp
		\end{equation}

@@

\begin{align} \begin{split}  
	\vec{C} = c(\vec{pw}, \vec{sc}, \vec{rsc}, \vec{uv}) = 
		& \sum_{mdc} cw_{m} (pw_{mdc}) +  \\
		& \sum_{tdc} cw_{M} (ps_{tMdc}) (\text{ to prevent infinite rescheduling })+ \\
		& + cc \sum_{tt`mdc, \text{where } t' > t} rsc_{tt'mdc} - cc \sum_{tt`mdc, \text{where } t' < t} rsc_{tt'mdc} + \\ 
		& + M (uv_{tp})
\end{split} \end{align} 
$cw_{m}$ is computed as follows ($val$ is arbitrary number that describes cost growth):
	\begin{equation}  cw_{m} = val^m \quad \forall m \end{equation} 
$cc$ is some arbitrary value

@@

\subsection{Generating an Action}
Once $\vec{\beta}$ values have been approximated, you may use the model below to generate a recommended action for a specific state.
\begin{equation}
	\min_{\vec{A}} c(\vec{S}, \vec{A}) + E[V]
\end{equation}
Subject to:
all constraints in section "\nameref{action constraints}"

>>>>

\subsubsection{Action Constraints}
\label{action constraints}
\begin{itemize}
    \item Tracks PPE Usage  
    \begin{itemize}
    		\item ($U_{pdc}$ - usage of PPE $p$ per patient difficulty $d$, CPU $c$)
    \end{itemize}
        \begin{equation} 
			(\sum_{mdc}ps_{tmdc} + \sum_{mdc}sc_{tmdc} + 
			\sum_{tmdc} rsc_{tt'mdc} - \sum_{t'mdc} rsc_{tt'mdc})U_{pdc} = uu_{tp}\ \quad \forall tp
		\end{equation}

@@

\begin{align} \begin{split}  
	\vec{C} = c(\vec{pw}, \vec{sc}, \vec{rsc}, \vec{uv}) = 
		& \sum_{mdc} cw_{m} (pw_{mdc} - \sum_{t} sc_{tmdc}) +  \\
		& \sum_{tdc} cw_{M} (ps_{tMdc}) (\text{ to prevent infinite rescheduling })+ \\
		& + cc \sum_{tt`mdc, \text{where } t' > t} rsc_{tt'mdc} - cc \sum_{tt`mdc, \text{where } t' < t} rsc_{tt'mdc} + \\ 
		& + M (uv_{tp})
\end{split} \end{align} 
$cw_{m}$ is computed as follows ($val$ is arbitrary number that describes cost growth):
	\begin{equation}  cw_{m} = val^m \quad \forall m \end{equation} 
$cc$ is some arbitrary value

@@

\subsection{Generating an Action}
Once $\vec{\beta}$ values have been approximated, you may use the model below to generate a recommended action for a specific state.
\begin{equation*}
	\min_{\vec{A}} c(\vec{S}, \vec{A}) - \gamma v(S')
\end{equation*}	
\begin{align*}
	v(S') = \bigg(  & \beta^0 + \sum_{t=2p}^{T} \beta_{tp}^{ue} uen_{p} + \\ 
	& \sum_{p} \beta_{1p}^{ue} \Big( uen_{p} + ue_{1p} - uu_{1p} - 
		\sum_{dc} U_{pdc} (\sum_{m} sc_{1mdc} + \sum_{t'm} rsc_{1t'mdc} - \sum_{tm} rsc_{t1mdc}) \Big) + \\
	& \sum_{tp}^{T-1} \beta_{tp}^{uu} \Big( uu_{t+1p} + 
		\sum_{mdc} ps_{tmdc}pwp_{} (U_{pd+1c} - U_{pdc}) + 
		U_{pdc} \big( \sum_{mdc} sc_{t+1}  - \sum_{t'mdc} rsc_{t+1t'} + 
		\sum_{tmdc} rsc_{tt'+1} \big) \Big) + \\
	& \sum_{dc} \beta_{0dc}^{pw} E[pea_{dc}]) + \\
	& \sum_{m=1,dc}^{M-1} \beta_{mdc}^{pw} \Big( pw_{m-1dc} (1 - pwp) + pw_{m-1d-1c} pwp - \sum_{t} sc_{tm-1dc} \Big) + \\
	& \sum_{dc} \beta_{Mdc}^{pw} \sum_{M-1}^{M} \Big( pw_{mdc} (1 - pwp) + pw_{md-1c} pwp - \sum_{t} sc_{tmdc} \Big) + \\
	& \sum _{t=1 m=1 dc}^{T-1 M-1} \beta_{tmdc}^{ps} 
		\Big( ps_{t+1m-1dc}(1-pwp) + ps_{t+1m-1d-1c} pwp - \sum_{t} sc_{t+1m-1dc} - \\
		& - \sum_{t'} rsc_{t+1t'm-1dc} + \sum_{t} rsc_{tt'+1m-1dc} \Big) + \\
	& \sum _{t=1dc}^{T-1} \beta_{tMdc}^{ps} \sum_{M-1}^{M} \Big( ps_{t+1mdc}(1-pwp) + ps_{t+1md-1c} pwp - \sum_{t} sc_{t+1mdc} \\ 
	&  - \sum_{t'} rsc_{t+1t'mdc} + \sum_{t} rsc_{tt'+1mdc} \Big) \bigg)
	& \bigg)
\end{align*}
Subject to:
all constraints in section "\nameref{action constraints}"
